---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# brfssIA

<!-- badges: start -->
<!-- badges: end -->

The goal of brfssIA is to ...

## Installation

You can install the development version of brfssIA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("heike/brfssIA")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(brfssIA)
library(tidyverse)
## basic example code
data(brfss13IA)

brfss13IA %>% count(DIABETE3)
```

## Provenance of the data

The datasets brfss13IA to brfss21IA are subsets of the [annual BRFSS surveys](https://www.cdc.gov/brfss/annual_data/annual_data.htm).

The code below shows the download of the 2021 BRFSS responses from the CDC's website and the successive filter on respondents from Iowa only:

```{r eval = FALSE}
path_zip <- "https://www.cdc.gov/brfss/annual_data/2021/files/LLCP2021XPT.zip"
download.file(path_zip, destfile="brfss.zip", mode="wb")
contains <- unzip("brfss.zip", list=TRUE) # just look  
unzip("brfss.zip", exdir="brfss") # unzip into directory brfss

xpt_file <- dir("brfss", pattern=".XPT")
library(foreign)
# Read in the SAS data
brfss <- foreign::read.xport(xpt_file)

# Iowa has the FIPS code 19
iowa <- brfss %>% filter(X_STATE==19)
# this data set was saved as object brfssIA21
```

#### Data source:

Centers for Disease Control and Prevention (CDC). Behavioral Risk Factor Surveillance System Survey Data. Atlanta, Georgia: U.S. Department of Health and Human Services, Centers for Disease Control and Prevention, 2013-2021.
